A Framework for Predictable Actor-Critic Control

### 2022-05-09 documentation/paper.tex
-
improve math stuff

@@

    % 
    % 
    % 
    % Acknowledgments
    % 
    % 
    % 
    \begin{ack}
        FIXME
        Do {\bf not} include this section in the anonymized submission, only in the final paper.

        Use unnumbered first level headings for the acknowledgments.
        All acknowledgments go at the end of the paper before the list of references.
        - declare funding (financial activities supporting the submitted work)
        - competing interests (related financial activities outside the submitted work)
    \end{ack}

>>>>

    % 
    % epsilon optimizer
    % 
    \begin{algorithm}[h]

        \newcommand{\planlensPerEpsilon}{planlens_\epsilon}
        \newcommand{\discountedRewards}{discounted\_rewards}
        \newcommand{\sampledRewards}{sampled\_rewards}
        \newcommand{\sum}{\sigma}
        \newcommand{\minimumAcceptableReward}{b_{lower}}
        \newcommand{\numberOfbaselineSamples}{b_{sz}}
        \newcommand{\initialEpsilon}{\epsilon_{i}}
        \newcommand{\runningEpsilon}{\epsilon_{r}}
        \newcommand{\finalEpsilon}{\epsilon_{o}}
        \newcommand{\allEpsilons}{a_\epsilon}
        \newcommand{\intialHorizon}{\h_{i}}
        \newcommand{\finalHorizon}{\h_{o}}
        \newcommand{\planLengths}{planlens}

        % \SetAlgoLined\
        \SetKwInOut{Input}{Input}
        \SetKwInOut{Output}{Output}
        \Input{
            $\mathrm{\minimumAcceptableReward}$, minimum acceptable reward \\
            $\mathrm{iter}$ , number of iterations of refinement \\
            $\mathrm{inc}$, scale multiplier for epsilon \\
            $\mathrm{\numberOfbaselineSamples}$, number of baseline samples \\
            $\mathrm{b_{min}}$, min confidence interval of baseline \\
            $\mathrm{b_{ci}}$, baseline confidence interval width \\
            $\mathrm{ci_{lvl}}$, confidence level  \\
            $\mathrm{\initialEpsilon}$, initial epsilon \\
            $\mathrm{\intialHorizon}$, initial horizon \\
        }
        \Output{
            \\
            $\mathrm{\finalEpsilon}$, a refined epsilon\\
            $\mathrm{\finalHorizon}$, a refined horizon\\
        }
        \caption{Find Epsilon}
        \label{algo:find_epsilon}
        \vspace{8pt}

        \(\runningEpsilon \gets  \initialEpsilon \) \\
        \(\allEpsilons \gets []\) \# empty array \\
        \(\planlensPerEpsilon \gets \{\}\) \# empty hashmap \\
        \# Note: requesting a non-existent key for this hash-map returns an array containing $\intialHorizon$ \\
        \For{$i$ in $[0,..., iter]$}{
            % \label{ln:loopplan1}
            \(\sampledRewards \gets []\) \# empty array \\
            \For{$j$ in $[0,..., \numberOfbaselineSamples]$}{
                % \label{ln:loopsample1}
                $\discountedRewards, \planLengths \gets runEpisode(\epsilon=\runningEpsilon)$ 
                $\sampledRewards.push(\sum(\discountedRewards))$ 
                $\planlensPerEpsilon[\runningEpsilon] \gets concat(\planlensPerEpsilon[\runningEpsilon], \planLengths)$ 
                \If{$length(\sampledRewards) < 2$} {
                    $continue$
                }

                $s_{max}, s_{min} \gets confidenceInterval(ci_{lvl}, \sampledRewards)$
                $s_{ci} \gets s_{max} - s_{min}$
                \If{$s_{max} < \minimumAcceptableReward \texttt{or} s_{ci} < b_ci$}{
                    $break$
                }
            }

            \If{$mean(\sampledRewards) \geq \minimumAcceptableReward$}{
                $\runningEpsilon \gets \runningEpsilon \* inc$
            }{
                $\runningEpsilon \gets \runningEpsilon / inc$
            }

            $\allEpsilons.push(\runningEpsilon)$
        }
        $\finalEpsilon \gets median(\allEpsilons)$

        $\finalHorizon \gets max(median(\planlensPerEpsilon[\finalEpsilon]), 1) * 2$

        \Return{
            $\mathrm{\finalEpsilon}$
            $\mathrm{\finalHorizon}$
        }
    \end{algorithm}

@@

    % 
    % 
    % 
    % Acknowledgments
    % 
    % 
    % 
        % \begin{ack}
        %     FIXME
        %     Do {\bf not} include this section in the anonymized submission, only in the final paper.

        %     Use unnumbered first level headings for the acknowledgments.
        %     All acknowledgments go at the end of the paper before the list of references.
        %     - declare funding (financial activities supporting the submitted work)
        %     - competing interests (related financial activities outside the submitted work)
        % \end{ack}
